brados: declarative, programmable object storage

### 2016-05-25 paper.tex
update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

The Brados language corresponds to a subset of the Bloom language which a
declarative language for expressing distributed programs as an unordered set
of rules. These rules fully specify program semantics and allow a programmer
to ignore the details associated with how a program is evaluated. This level
of abstraction is attractive for building storage interfaces whose portability
and correctness is critical.

@@

Brados models the storage system state uniformly as a collection of
relations~\cite{alvaro:cidr11}. The composition of a collection of existing
interfaces is then expressed as a collection of high-level \emph{queries} that
describe how a stream of requests (API calls) are filtered, transformed and
combined with existing state to define streams of outputs (API call returns as
well as updates to system state).  Separating the relational semantics of such
compositions from details of their physical implementations introduces a
number of degrees of freedom, similar to the ``data independence'' offered by
database query languages.  The choice of access methods (for example, whether
to use a bytestream interface or a key/value store), storage device classes
(e.g., whether to use HDDs or SDDs), physical layout details (e.g. a 1:1 or
N:1 mapping) and execution plans (e.g. operator ordering) can be postponed to
execution time.  The optimal choices for these physical design details are
likely to change much more often than the logical specification, freeing the
interface designer from the need to rewrite systems and device and interface
characteristics change.

@@

Amazingly these few code snippets express the semantics of the entire storage
device interface requirements in CORFU. For reference the ZLog implementation
of the CORFU storage interface in C++ comprises nearly 700 lines of code and
was designed to store log entries and metadata in the key-value interface,
thus requiring a lengthy rewrite to realize the performance advantage
available by using the bytestream interface, as was highlighted in
Section~\ref{sec:pd}. Furthermore, the complexity introduced by using the
bytestream interface would grow the amount of code written in the optimized
version.

>>>>

The Brados language corresponds to a subset of the Bloom language which a
declarative language for expressing distributed programs as an unordered set
of rules~\cite{alvaro:cidr11}. These rules fully specify program semantics and allow a programmer
to ignore the details associated with how a program is evaluated. This level
of abstraction is attractive for building storage interfaces whose portability
and correctness is critical.

@@

Brados models the storage system state uniformly as a collection of
relations. The composition of a collection of existing
interfaces is then expressed as a collection of high-level \emph{queries} that
describe how a stream of requests (API calls) are filtered, transformed and
combined with existing state to define streams of outputs (API call returns as
well as updates to system state).  Separating the relational semantics of such
compositions from details of their physical implementations introduces a
number of degrees of freedom, similar to the ``data independence'' offered by
database query languages.  The choice of access methods (for example, whether
to use a bytestream interface or a key/value store), storage device classes
(e.g., whether to use HDDs or SDDs), physical layout details (e.g. a 1:1 or
N:1 mapping) and execution plans (e.g. operator ordering) can be postponed to
execution time.  The optimal choices for these physical design details are
likely to change much more often than the logical specification, freeing the
interface designer from the need to rewrite systems and device and interface
characteristics change.

@@

Amazingly these few code snippets express the semantics of the entire storage
device interface requirements in CORFU. For reference our prototype
implementation of CORFU in Ceph (called
ZLog\footnote{https://github.com/noahdesu/zlog})
is written in C++ and the storage interface component comprises nearly 700
lines of code. This version
was designed to store log entries and metadata in the key-value interface,
thus requiring a lengthy rewrite to realize the performance advantage
available by using the bytestream interface, as was highlighted in
Section~\ref{sec:pd}. Furthermore, the complexity introduced by using the
bytestream interface would grow the amount of code written in the optimized
version.
